Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-11-05 WSSSPE4_report/WSSSPE4_report.tex
adding mission and vision text, mostly from Lorraine

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ \note{info needed}}

@@

\note{Lorraine and Dan will write this}

\todo{write info about process}

After this process, the final statements about WSSSPE are:

>>>>

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu}

@@

\note{by Lorraine and Dan}

Going into WSSSPE4, the WSSSPE organization had not had a formal mission or vision statement.
The organizers developed a strawhorse, which was presented to the participants early in the meeting.
The presentation included guidelines as well as examples from other similar communities.
The guidelines were that in general, an organization's mission should stand the test of time and state what is wrong and how the organization is going to fix it; Its vision should imagine what the world look like if the organization is successful; and from which, focus areas could be use to establish the scope of the organization along with its goals.

The participants were given time after the presentation to write down their comments.
Seven people volunteered to work on revising the mission and vision statements, incorporating these comments and presenting back to the community.
Based on this feedback, the committee redrafted the mission and vision.
The committee added focus areas to clarify the organizations breadth and to keep the mission and vision simple and long-lasting.
Comments after the close of the meeting were incorporated into the statements.

A final draft was put on GitHub (\url{https://github.com/WSSSPE/mission-vision}) and advertised
via the WSSSPE mailing list, Facebook group, and Twitter.
After 2 weeks without suggested changes, the final statements, as shown below, were added
to the WSSSPE web page (\url{http://wssspe.researchcomputing.org.uk/about-wssspe/}).
